When does VPD drive or reduce ET?

### 2017-10-20 doc/glab_meeting_2017-10-20/vpd.tex
rough draft done, as is spellcheck

\usepackage[english]{babel}
 % \usepackage[utf8x]{inputenc}
\usepackage[style=authoryear]{biblatex}
\addbibresource{references.bib}

@@

\section{Results}
\begin{frame}{Scaling Term}
  \[\frac{\partial \;  ET}{\partial \; D} = \mathbf{ \frac{g_a \; P}{T(\Delta + \gamma)} }   \left(\frac{ c_p}{R_{air}} - \frac{\text{LAI$_{ref}$}}{\text{LAI}} \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right) \right)\]
\begin{figure}
  \includegraphics[width=3.5in]{scaling.png}
  % \caption{}
\end{figure}
\end{frame}

@@

>>>>

\usepackage[english]{babel}
 % \usepackage[utf8x]{inputenc}
\usepackage[style=authoryear]{biblatex}
\addbibresource{references.bib}
\usepackage{tikz}

@@

\section{Results - theory}
\begin{frame}{Scaling Term}
  \[\frac{\partial \;  ET}{\partial \; D} = \mathbf{ \frac{g_a \; P}{T(\Delta + \gamma)} }   \left(\frac{ c_p}{R_{air}} - \frac{\text{LAI$_{ref}$}}{\text{LAI}} \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right) \right)\]
\begin{figure}
  \includegraphics[width=3.5in]{scaling.png}
  % \caption{}
\end{figure}
\end{frame}

@@

\section{Results - reality}
{ % all template changes are local to this group.
    \setbeamertemplate{navigation symbols}{}
    \begin{frame}[plain]{Idealized results - CRO}
        \begin{tikzpicture}[remember picture,overlay]
            \node[at=(current page.center)] {
                \includegraphics[width=\paperwidth]{cro_ideal.png}
            };
        \end{tikzpicture}
     \end{frame}
}

{ % all template changes are local to this group.
    \setbeamertemplate{navigation symbols}{}
    \begin{frame}[plain]{Results with uncertainty - CRO}
        \begin{tikzpicture}[remember picture,overlay]
            \node[at=(current page.center)] {
                \includegraphics[width=\paperwidth]{cro.png}
            };
        \end{tikzpicture}
     \end{frame}
}

{ % all template changes are local to this group.
    \setbeamertemplate{navigation symbols}{}
    \begin{frame}[plain]{Idealized results - CSH}
        \begin{tikzpicture}[remember picture,overlay]
            \node[at=(current page.center)] {
                \includegraphics[width=\paperwidth]{csh_ideal.png}
            };
        \end{tikzpicture}
     \end{frame}
}

{ % all template changes are local to this group.
    \setbeamertemplate{navigation symbols}{}
    \begin{frame}[plain]{Results with uncertainty - CSH}
        \begin{tikzpicture}[remember picture,overlay]
            \node[at=(current page.center)] {
                \includegraphics[width=\paperwidth]{csh.png}
            };
        \end{tikzpicture}
     \end{frame}
}

{ % all template changes are local to this group.
    \setbeamertemplate{navigation symbols}{}
    \begin{frame}[plain]{Idealized results - DBF}
        \begin{tikzpicture}[remember picture,overlay]
            \node[at=(current page.center)] {
                \includegraphics[width=\paperwidth]{dbf_ideal.png}
            };
        \end{tikzpicture}
     \end{frame}
}

{ % all template changes are local to this group.
    \setbeamertemplate{navigation symbols}{}
    \begin{frame}[plain]{Results with uncertainty - DBF}
        \begin{tikzpicture}[remember picture,overlay]
            \node[at=(current page.center)] {
                \includegraphics[width=\paperwidth]{dbf.png}
            };
        \end{tikzpicture}
     \end{frame}
   }

{ % all template changes are local to this group.
    \setbeamertemplate{navigation symbols}{}
    \begin{frame}[plain]{Idealized results - ENF}
        \begin{tikzpicture}[remember picture,overlay]
            \node[at=(current page.center)] {
                \includegraphics[width=\paperwidth]{enf_ideal.png}
            };
        \end{tikzpicture}
     \end{frame}
}

{ % all template changes are local to this group.
    \setbeamertemplate{navigation symbols}{}
    \begin{frame}[plain]{Results with uncertainty - ENF}
        \begin{tikzpicture}[remember picture,overlay]
            \node[at=(current page.center)] {
                \includegraphics[width=\paperwidth]{enf.png}
            };
        \end{tikzpicture}
     \end{frame}
   }

{ % all template changes are local to this group.
    \setbeamertemplate{navigation symbols}{}
    \begin{frame}[plain]{Idealized results - GRA}
        \begin{tikzpicture}[remember picture,overlay]
            \node[at=(current page.center)] {
                \includegraphics[width=\paperwidth]{gra_ideal.png}
            };
        \end{tikzpicture}
     \end{frame}
}

{ % all template changes are local to this group.
    \setbeamertemplate{navigation symbols}{}
    \begin{frame}[plain]{Results with uncertainty - GRA}
        \begin{tikzpicture}[remember picture,overlay]
            \node[at=(current page.center)] {
                \includegraphics[width=\paperwidth]{gra.png}
            };
        \end{tikzpicture}
     \end{frame}
   }

   \begin{frame}{Summary statistics}
     \begin{table}
       \caption{Statistics of $\frac{\partial \; ET}{\partial \; D}$ as a function of PFT.}
       \centering
       \begin{tabular}{l c c}
         \hline
         PFT & $\overline{\frac{\partial \; ET}{\partial \; VPD}}$ & fraction $\frac{\partial \; ET}{\partial \; VPD} < 0.$ \\
         \hline
         CRO & 0.000853  & 0.473311\\
         CSH & -0.108234 & 0.931660\\
         DBF & -0.012727 & 0.461674\\
         ENF & -0.034087 & 0.534425\\
         GRA & -0.019637 & 0.631735\\
         \hline
         \multicolumn{2}{l}{}  
       \end{tabular}
     \end{table}
   \end{frame}

\section{Conclusions}
\begin{frame}{Summary}
  \begin{itemize}
  \item Theory suggests that the ``tipping'' point for which atmospheric demand overwhelms plant response will be almost exclusively a function of VPD.  Plant types evolved to conserve water (CSH) have a higher VPD$_{crit}$ (and more negative ET response) than plants evolved (or bred) to use water and prioritize GPP (CRO).
  \item On average, ecosystem response to VPD follows roughly what we might expect: CRO (prioritize GPP) has postive ET response to VPD, while all others have a negative response. Ordering by increasing magnitude of negative reponse gives: DBF, GRA, ENF, CSH; which might seem to correspond to expectations for increasing water conservation as a function of PFT..
  \item Uncertainty is high, expecially for CRO and GRA. However, inclusion of uncertainty does not change the story for ENF or CSH.
  \end{itemize}
\end{frame}
